Singapore's Public Housing Affordability

### 2023-11-15 datastory.qmd
Project Update

So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable! Soon, it will be time for you to consider purchasing a new home so let's play a little game.

@@

<iframe height="750" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">

>>>>

So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable! Soon, it will be time for you to consider purchasing a new home so let's play a little game!

@@

<iframe height="700" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
